\documentclass[a4paper]{article}
\usepackage[english]{babel}
\usepackage{pdfpages, titling}

\usepackage{array, float}
\usepackage{cite, amsmath, tablefootnote}
\usepackage{graphicx, caption, subfigure, wrapfig}
\usepackage{listings}
\usepackage{color}

\newcommand{\subtitle}[1]{%
  \posttitle{%
    \par\end{center}
    \begin{center}\large#1\end{center}
    \vskip0.5em}%
}
\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}

\author{Eva van Weel() and Jaromir Camphuijsen (6042473)}
\date{\today}
\title{Mystery Dataset}
\subtitle{}
\begin{document}
\maketitle


\tableofcontents


\newpage
\section{Introduction}
Background, overview of relevant literature, structure of remainder of the report

Introduce the problem that you have studied
–Describe what others have done (related work)
–Describe the structure of your report
•Make sure that you include enough and appropriate references.
–Explain for each referenced paper why it is relevant for your paper.
•In some cases, depending on the size of each part, the problem statement and the related work should be made into separate sections or chapters.

\section{Core (multiple sections)}
Your report must clearly explain what it is about, and should not just be a repository of facts.
•The structure of this part depends on the nature of your work. E.g.:
–Start by describing your methods and algorithms
•Use formulae, pseudo-code
–Describe the implementation
•Describe import choices, leave out what should be self-evident
•But (well documented) source code goes to appendices, if to be included at all
–Describe your experiment and the results
–Interpret your results
•As with the introduction, the core may be split into separate sections, like methods, experimentation and interpretation of the results.

\section{conclusions}
In this section you give a clear resume of the conclusions from your work and discuss its relation to previous research.
–For that reason, some authors will actually put the section on related work after the core section(s)
–The conclusions should reflect back on the original problem statement in your introduction.
•When applicable, your work may result in suggestions on how to further validate or extend your research.


\bibliography{REPORTbib}
\bibliographystyle{ieeetr}
\end{document}